\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-28 manuscript.Rnw
Some style updates to captions

%% other packages
\usepackage{graphicx}
\usepackage{subcaption} 
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{algorithm}
\caption{Simulation of individual continuous time state transition model}
\label{alg:sim-ictstm}
\begin{enumerate}
\item Let $r$ be the state entered at time $t_j$. The number of permitted transitions from state $r$ is given by $n_r$. If $j=0$, then $t_j = 0$. 
\item Simulate times $\mathcal{T} = \{t_{1, j+1}, t_{2, j+1}, \ldots t_{n_r, j+1}\}$ to each of the $n_r$ permitted transitions.
\item Set the time of the transition $t_{j+1}$ equal to the minimum simulated time in $\mathcal{T}$ and the next state $s$ to the state with the minimum simulated time.
\item Set $r=s$ and $t_j = t_{j+1}$. If the patient is still alive, repeat the previous steps until death.
\end{enumerate}
\end{algorithm}

@@

\end{tikzpicture}
\caption{Economic modeling process}\label{fig:econ-eval-process-hesim}
\end{figure}

@@

\begin{table} [h]
\caption{Parameterization of disease models}\label{tbl:parameterize-disease-model}
\footnotesize
\begin{tabular*}{\textwidth}{l l l l}
\hline
Economic model & Statistical model & Parameter object & Model object\\
\hline
\code{CohortDtstm} & Custom & \code{tparams_transprobs} & \code{msm::msm} \\
 & Multinomial logistic regressions & \code{params_mlogit} & \code{multinom_list}\\
\code{IndivCtstm} & Multi-state model (joint likelihood) & \code{params_surv} & \code{flexsurv::flexsurvreg}\\
& Multi-state model (transition-specific) & \code{params_surv_list} & \code{flexsurvreg_list}\\
\code{Psm} & Independent survival models & \code{param_surv_list} & \code{flexsurvreg_list}\\
\hline
\end{tabular*}
\end{table}

@@

\begin{table} [h]
\caption{Parameterization of state value models}\label{tbl:parameterize-stateval-model}
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Statistical model & Parameter object & Model object\\
\hline
Predicted means & \code{tparams_mean} & \code{stateval_tbl}\\
Linear model & \code{params_lm} & \code{stats::lm}\\
\hline
\end{tabular*}
\end{table}

@@

\begin{table} [h]
\caption{Submodels comprising an economic model}\label{tbl:submodels}
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Economic model & Disease model & Utility model & Cost model(s)\\
\hline
\code{CohortDtstm} & \code{CohortDtstmTrans} & \code{StateVals} & \code{StateVals}\\
\code{IndivCtstm} & \code{IndivCtstmTrans} & \code{StateVals} & \code{StateVals}\\
\code{Psm} & \code{PsmCurves} & \code{StateVals} & \code{StateVals}\\
\hline
\end{tabular*}
\end{table}

@@

\begin{table} [h]
\caption{Methods for simulating outcomes from economic models}\label{tbl:simulate-outcomes}
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Economic model & Disease progression  & QALYs & Costs \\
\hline
\code{CohortDtstm} & \code{sim_stateprobs()} & \code{sim_qalys()} & \code{sim_costs()}\\
\code{IndivCtstm} & \code{sim_disease()}, \code{sim_stateprobs()}  & \code{sim_qalys()} & \code{sim_costs()}\\
\code{Psm} & \code{sim_survival()}, \code{sim_stateprobs()}  & \code{sim_qalys()} & \code{sim_costs()}\\
\hline
\end{tabular*}
\end{table}

@@

\end{tikzpicture}
\caption{Three state model of disease progression in oncology}\label{fig:three-state-model}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics{figure/ictstm_plot_stateprobs-1.pdf}
\caption{Mean simulated state probabilities from the probabilistic sensitivity analysis} \label{fig:ictstm-stprobs}
\end{figure}

@@

\begin{figure}[t!]
\centering
% Cost-effectiveness plane
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ce_plane-1.pdf}
\caption{Cost-effectiveness plane} \label{subfig:ce-plane}
\end{subfigure}
% CEAC (simultaneous)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-1.pdf}
\caption{CEAC (simultaneous)} \label{subfig:ceac-simultaneous}
\end{subfigure}
\par\bigskip % Add some vertical space for second row
% CEAC (pairwise)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-2.pdf}
\caption{CEAC (pairwise)} \label{subfig:ceac-pw}
\end{subfigure}
% CEAF
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceaf-1.pdf}
\caption{CEAF} \label{subfig:ceaf}
\end{subfigure}
\par\bigskip % Add some vertical space for third row
% EVPI
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/evpi-1.pdf}
\caption{EVPI} \label{subfig:evpi}
\end{subfigure}
\caption{Representations of decision uncertainty}\label{fig:cea-plots}
\end{figure}

>>>>

%% other packages
\usepackage{graphicx}
\usepackage{subcaption} 
\usepackage{algorithm}
\captionsetup[algorithm]{labelfont=rm,labelsep=colon}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{caption} 
\captionsetup[table]{skip=5pt}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\begin{algorithm}
\caption{Simulation of individual continuous time state transition model.}
\label{alg:sim-ictstm}
\begin{enumerate}
\item Let $r$ be the state entered at time $t_j$. The number of permitted transitions from state $r$ is given by $n_r$. If $j=0$, then $t_j = 0$. 
\item Simulate times $\mathcal{T} = \{t_{1, j+1}, t_{2, j+1}, \ldots t_{n_r, j+1}\}$ to each of the $n_r$ permitted transitions.
\item Set the time of the transition $t_{j+1}$ equal to the minimum simulated time in $\mathcal{T}$ and the next state $s$ to the state with the minimum simulated time.
\item Set $r=s$ and $t_j = t_{j+1}$. If the patient is still alive, repeat the previous steps until death.
\end{enumerate}
\end{algorithm}

@@

\end{tikzpicture}
\caption{Economic modeling process.}\label{fig:econ-eval-process-hesim}
\end{figure}

@@

\begin{table} [h]
\footnotesize
\begin{tabular*}{\textwidth}{l l l l}
\hline
Economic model & Statistical model & Parameter object & Model object\\
\hline
\code{CohortDtstm} & Custom & \code{tparams_transprobs} & \code{msm::msm} \\
 & Multinomial logistic regressions & \code{params_mlogit} & \code{multinom_list}\\
\code{IndivCtstm} & Multi-state model (joint likelihood) & \code{params_surv} & \code{flexsurv::flexsurvreg}\\
& Multi-state model (transition-specific) & \code{params_surv_list} & \code{flexsurvreg_list}\\
\code{Psm} & Independent survival models & \code{param_surv_list} & \code{flexsurvreg_list}\\
\hline
\end{tabular*}
\caption{Parameterization of disease models.}\label{tbl:parameterize-disease-model}
\end{table}

@@

\begin{table} [h]
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Statistical model & Parameter object & Model object\\
\hline
Predicted means & \code{tparams_mean} & \code{stateval_tbl}\\
Linear model & \code{params_lm} & \code{stats::lm}\\
\hline
\end{tabular*}
\caption{Parameterization of state value models.}\label{tbl:parameterize-stateval-model}
\end{table}

@@

\begin{table} [h]
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Economic model & Disease model & Utility model & Cost model(s)\\
\hline
\code{CohortDtstm} & \code{CohortDtstmTrans} & \code{StateVals} & \code{StateVals}\\
\code{IndivCtstm} & \code{IndivCtstmTrans} & \code{StateVals} & \code{StateVals}\\
\code{Psm} & \code{PsmCurves} & \code{StateVals} & \code{StateVals}\\
\hline
\end{tabular*}
\caption{Submodels comprising an economic model.}\label{tbl:submodels}
\end{table}

@@

\begin{table} [h]
\footnotesize
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l l l}
\hline
Economic model & Disease progression  & QALYs & Costs \\
\hline
\code{CohortDtstm} & \code{sim_stateprobs()} & \code{sim_qalys()} & \code{sim_costs()}\\
\code{IndivCtstm} & \code{sim_disease()}, \code{sim_stateprobs()}  & \code{sim_qalys()} & \code{sim_costs()}\\
\code{Psm} & \code{sim_survival()}, \code{sim_stateprobs()}  & \code{sim_qalys()} & \code{sim_costs()}\\
\hline
\end{tabular*}
\caption{Methods for simulating outcomes from economic models.}\label{tbl:simulate-outcomes}
\end{table}

@@

\end{tikzpicture}
\caption{Three state model of disease progression in oncology.}\label{fig:three-state-model}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics{figure/ictstm_plot_stateprobs-1.pdf}
\caption{Mean simulated state probabilities from the probabilistic sensitivity analysis.} \label{fig:ictstm-stprobs}
\end{figure}

@@

\begin{figure}[t!]
\centering
% Cost-effectiveness plane
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ce_plane-1.pdf}
\caption{Cost-effectiveness plane} \label{subfig:ce-plane}
\end{subfigure}
% CEAC (simultaneous)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-1.pdf}
\caption{CEAC (simultaneous)} \label{subfig:ceac-simultaneous}
\end{subfigure}
\par\bigskip % Add some vertical space for second row
% CEAC (pairwise)
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceac-2.pdf}
\caption{CEAC (pairwise)} \label{subfig:ceac-pw}
\end{subfigure}
% CEAF
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/ceaf-1.pdf}
\caption{CEAF} \label{subfig:ceaf}
\end{subfigure}
\par\bigskip % Add some vertical space for third row
% EVPI
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{figure/evpi-1.pdf}
\caption{EVPI} \label{subfig:evpi}
\end{subfigure}
\caption{Representations of decision uncertainty.}\label{fig:cea-plots}
\end{figure}
